Discussion

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added lil info about h7

Almost all participants showed an absolute preference for a particular strategy, indicated by an SV of 1. 
We also found a wide range of SVs (between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`), suggesting that individuals have varying degrees of strategy preference.
There was a significant relationship between SVs and strategy choice. 
Overly frequent, persons chose the strategy for which the highest subjective value had been determined before, supporting hypothesis H7.
We also found associations between individual SVs and various predictors.
Subjective effort, utility, and *corrugator* muscle activity significantly predicted individual SVs.
Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
However, individual SVs did not show associations with self-reported ER flexibility, we therefore found no evidence for hypothesis H7.
In a subsequent exploratory analyses, we found associations between individual SVs and self-control.
This is consistant with the literature, which has already reported correlations between self-control and demand avoidance[@Kool2013].
However, we did not find an association between NFC and SVs. 
This is in contrast to the literature, which has reported correlations between NFC, effort discounting and demand avoidance[@ZernaScheffel2022;@Westbrook2013].
However, these were all cognitive tasks. The role of NFC in affective tasks is not yet known.

>>>>

Almost all participants showed an absolute preference for a particular strategy, indicated by an SV of 1. 
We also found a wide range of SVs (between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`), suggesting that individuals have varying degrees of strategy preference.
There was a significant relationship between SVs and strategy choice. 
Overly frequent, persons chose the strategy for which the highest subjective value had been determined before, supporting hypothesis H7.
We also found associations between individual SVs and various predictors.
Subjective effort, utility, and *corrugator* muscle activity significantly predicted individual SVs.
Contrary to our hypothesis H6, utility and not effort was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
However, individual SVs did not show associations with self-reported ER flexibility, we therefore found no evidence for hypothesis H7.
In a subsequent exploratory analyses, we found associations between individual SVs and self-control.
This is consistant with the literature, which has already reported correlations between self-control and demand avoidance[@Kool2013].
However, we did not find an association between NFC and SVs. 
This is in contrast to the literature, which has reported correlations between NFC, effort discounting and demand avoidance[@ZernaScheffel2022;@Westbrook2013].
However, these were all cognitive tasks. The role of NFC in affective tasks is not yet known.
